---
title: "Merced River Redd Logistic Regression Output"
author: "Rosealea Bond"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  github_document:
    toc: true
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "readme-figs/"
)
```

## General Goals

The main goal is to preform a logistic regression invesigating redd presence (redd=1) and absence (redd=0). Potential parameters include depth, velocity, csi, wsg, dar, and site (Merced River Ranch (mrr) and Robinson Reach (rr)). The steps include generating a candidate set of models, run AIC, and additional statistics as needed. This analysis is simmilar to Benjankar et al., (2016). The GIT reporsiory can be found here https://github.com/RMBond/Merced_Redd_selection.git

      
**Description of Dataset:**  
Logistic Regression input file **mHabVarsSite.csv** was generated by L. Harrison on 14 February 2019. 
The script **Redd_logisticregression.R** was created to run the logistic regression analysis.

## Output
**All sites pooled together**  
```{r echo=FALSE, results='asis'}
library(knitr)
kable(hab.output[1:10,1:7], caption = "AIC ranking of all sites pooled together")
```


**Robinson Reach**  


**Merced River Ranch**  

## Next To Do's

1. Additional statistics? (Wald statistic?)
2. Look at residual plots

